---
title: "Test_R_markdown_shiny"
author: "Jackie"
date: "2025-03-28"
output: html_document
runtime: shiny
---

```{r load_libary, include=FALSE}
library(ggplot2)
library(readxl)
library(tidyverse)
library(lubridate)
library(data.table)
library(stringr)
library(shiny)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.


# Select the sites

Simple example of how to use this shiny function to print choice to the screen,
2 ways to do this:
* Without reactive step - easy
* With reactive so that the extra step can be used in other function in the document.

Just need to remember to make a reactive step first and the call the reactive function ()

For more information on reactive function see:

https://shiny.posit.co/r/getstarted/build-an-app/reactivity-essentials/reactives-observers.html

### Simple example of site selection

```{r sites_selction_simple_version, echo=FALSE}
# creating a data frame
list_of_sites <- data.frame(
    Name = c("Karoonda", "Wharminda", "Copeville", "Walpeup" , "Bute", "Balaklava", "Annuello"), ### add more here when you have the info
    Number = c("25006", "18113", "25003", "76065", "21012", "21002", "76000"),
    Latitude = c("-35.09", "-33.97", "-34.80", "-35.14",  "-33.86", "-34.14", "-34.85"),
    Longitude = c("139.90", "136.25", "139.85", "142.02", "138.01", "138.42", "142.78"),
    State = c("SA", "SA", "SA", "VIC","SA", "SA", "VIC")
    )

selectInput(inputId="site_number", 
            label = "Select site number:",
              choices = (c("25006", "18113", "25003", "76065", "21012", "21002", "76000")), 
            selected = "25006")

## how it works with out reactive ie the user selects the site and then we print it out

renderText({
    paste("You have selected", input$site_number)
  })

```

### Reactive example of site selection

```{r sites_selction_reactive_version, echo=FALSE}
## add reactive bit same as before but now we add a step to make the selection reactive - so it can be used in other function

reactive_site_selection <- reactive({
     input$site_number 
  })

renderText({
    paste("You have selected as reactive", reactive_site_selection()) ## this is the reactive call reactive()
  })



```


### use site selection to build a file path

File path and then append the site selected and print to document
"H:/Output-2/Analysis/Scripts/Jackie/Downloaded_files/Neater_file_"


I have white space in this example and I can't get rid of it!!

```{r sites_selction_reactive_file_path1, echo=FALSE}
## add reactive bit same as before but now we add a step to make the selection reactive - so it can be used in other function

reactive_site_selection <- reactive({
     input$site_number 
  })


file_path <-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Downloaded_files")

renderText({
    paste(file_path,"Neater_file_", 
          as.character(str_trim(reactive_site_selection())), ".csv") 
          #str_trim(reactive_site_selection()), ".csv") 
  })




```
### use downlaod handler 

Umm this doesnt do what I expected!
File path and then append the site selected and print to document
"H:/Output-2/Analysis/Scripts/Jackie/Downloaded_files/Neater_file_"


```{r sites_selction_reactive_file_path2, echo=FALSE}
## add reactive bit same as before but now we add a step to make the selection reactive - so it can be used in other function

reactive_site_selection <- reactive({
     input$site_number 
  })

#downloadButton("downlaodData", "Download")

downloadHandler(
  filename= function(){
    paste("H:/Output-2/Analysis/Scripts/Jackie/Downloaded_files/Neater_file_", reactive_site_selection(),
          ".csv", sep = "")
    },
  content = function(file){
        write.csv(data, file)
  }
)

```


## what about using a list of file?

```{r list_of_file1, echo=FALSE}

file_path <-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Downloaded_files")

# reactive_list_files <- list.files(path = file_path, 
#                          #pattern = ".csv",
#                          pattern = reactive_site_selection())

renderText({
    paste("files", list.files(path = file_path, 
                              pattern = reactive_site_selection()), recursive = TRUE)
  })

```


## Another idea??

```{r sites_selction_reactive_version2, echo=FALSE}
## add reactive bit same as before but now we add a step to make the selection reactive - so it can be used in other function

file_path <-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Downloaded_files")

reactive_site_selection_path <- reactive({
  paste0(file_path, 
         "/Neater_file_",
         input$site_number, 
         ".csv") 
  })

renderText({
    paste("Path for site selected as reactive", reactive_site_selection_path()) ## this is the reactive call reactive()
  })



```