---
title: "Step 4 Yield potential for current season"
author: "Jackie"
date: "2025-03-31"
output: html_document
---

```{r load_libary, include=FALSE}
library(ggplot2)
library(readxl)
library(tidyverse)
library(lubridate)
library(data.table)
library(stringr)
library(DT)
```

## Choose what site you want to create forecast yield for.


```{r list of sites, echo=FALSE}
list_of_sites <- data.frame(
    Name = c("Karoonda", "Wharminda", "Copeville", "Walpeup" , "Bute", "Balaklava", "Annuello"), ### add more here when you have the info
    Number = c("25006", "18113", "25003", "76065", "21012", "21002", "76000"),
    Latitude = c("-35.09", "-33.97", "-34.80", "-35.14",  "-33.86", "-34.14", "-34.85"),
    Longitude = c("139.90", "136.25", "139.85", "142.02", "138.01", "138.42", "142.78"),
    State = c("SA", "SA", "SA", "VIC","SA", "SA", "VIC")
    )

DT::datatable(list_of_sites)


 
```

## List of historical decile tables created in step 2
* Looking in this folder.
* If it is in another location change the bellow code chuck.(file_path_input_data)
* "//fs1-cbr.nexus.csiro.au/{af-sandysoils-ii}/work/Output-2/Analysis/Scripts/Jackie/Decile_tables"

```{r list of sites with decile tables, echo=FALSE}

 file_path_input_data<-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Decile_tables")

list_of_file <- list.files(path = file_path_input_data, pattern = ".csv")
list_of_file <- as.data.frame(list_of_file)
DT::datatable(list_of_file)
 
```
## Select the site number
* create a new variable in the below code chuck that will be used for the analysis
* Shiny application would be nice but then I have problem saving the output.

```{r sites_selction, echo=FALSE}
 site_selected <- "25006"
print(site_selected)
```
## Download the **daily met** file 
* use the daily met file to calculate the rain from start of growing season to defined date

```{r daily met file, echo=FALSE, warning=FALSE}
  daily_file <- read.csv(
    paste0(
    file_path_input_data,
         "/Daily_met_file_season types_",
         site_selected, 
         ".csv") )
daily_file <- daily_file %>% mutate(across(where(is.numeric), round, 2))

str(daily_file)
```
## Seasonally adjust dates.

* If the daily met file won't allow you to choose so many dates (ie the dates have not happened yet for that year).
* Make the dates the same for the subsequent defined date. 
* The report is expecting 7 dates, but maybe you only have 2 date, so you can fill out date1 and date2 with real dates that occur in the daily met file, the rest of the dates should then become the last know dates i.e. date2.
* You will need to **change the dates in the below code chunk** (if you don't want these).



```{r sites_selction_download GS file, echo=FALSE, warning=FALSE}

start <- "2024-04-01"

defined_date1 <- "2024-04-01"
defined_date2 <- "2024-05-28"
defined_date3 <- "2024-06-30"
defined_date4 <- "2024-07-24"
defined_date5 <- "2024-08-30"
defined_date6 <- "2024-09-30"
defined_date7 <- "2024-10-24"


### Filter dataset based on years 
daily_file1 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date1)))

daily_file2 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date2)))
daily_file3 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date3)))
daily_file4 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date4)))
daily_file5 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date5)))
daily_file6 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date6)))
daily_file7 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date7)))



daily_file_sum_rain1 <- daily_file1 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date1)
daily_file_sum_rain2 <- daily_file2 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date2)
daily_file_sum_rain3 <- daily_file3 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date3)
daily_file_sum_rain4 <- daily_file4 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date4)
daily_file_sum_rain5 <- daily_file5 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date5)
daily_file_sum_rain6 <- daily_file6 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date6)
daily_file_sum_rain7 <- daily_file7 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date7)

daily_file_sum_rain_all <- rbind(daily_file_sum_rain1,
                                 daily_file_sum_rain2,
                                 daily_file_sum_rain3,
                                 daily_file_sum_rain4,
                                 daily_file_sum_rain5,
                                 daily_file_sum_rain6,
                                 daily_file_sum_rain7)

rm(daily_file_sum_rain1,
   daily_file_sum_rain2,
   daily_file_sum_rain3,
   daily_file_sum_rain4,
   daily_file_sum_rain5,
   daily_file_sum_rain6,
   daily_file_sum_rain7,
   daily_file1,
   daily_file2,
   daily_file3,
   daily_file4,
   daily_file5,
   daily_file6,
   daily_file7)
### Summary of rain

DT::datatable(daily_file_sum_rain_all)

```


## Download the **Growing season** decile file 

```{r sites_selction_download gs file, echo=FALSE, warning=FALSE}
#GS_decile_table_df_25006 

 df_gs <- read.csv(
    paste0(
    file_path_input_data,
         "/GS_decile_table_df_",
         site_selected, 
         ".csv") )
df_gs <- df_gs %>% mutate(across(where(is.numeric), round, 2))

DT::datatable(df_gs)

```

## Download the **Summer** decile file 
```{r sites_selction_download summer file, echo=FALSE, warning=FALSE}
#summer_decile_table_df_25006

  df_summer <- read.csv(
    paste0(
    file_path_input_data,
         "/summer_decile_table_df_",
         site_selected, 
         ".csv") )
df_summer <- df_summer %>% mutate(across(where(is.numeric), round, 2))

DT::datatable(df_summer)

```




```{r D5_Starting water Baseline and Frontier, echo=FALSE}

# ## Decile 5 Summer start water baseline and frontier
# * This is calculated from the summer decile tables for the site nominated
# * Baseline Estimated Starting water is 25% of summer rainfall
# * Frontier Estimated Starting water is 30% of summer rainfall

# ## add a clm with this Estimated Starting water for all deciles
# df_summer <- df_summer %>%
#   mutate(Baseline_Estimated_Starting_water = summer_decile_max_rain * 0.25, # Estimated Starting water = (25% of Summer Rainfall)
#          Frontier_Estimated_Starting_water  = summer_decile_max_rain * 0.30) # Estimated Starting water = (30% of Summer Rainfall)
# 
# 
# ## create 2 new variable for decile 5 Baseline Estimated Starting water and Frontier Estimated Starting water
# 
# D5_Baseline_Est_Start_water <- df_summer %>% 
#   filter(summer_deciles_names =="decile_5" ) %>% 
#   select(Baseline_Estimated_Starting_water)
# 
# D5_Baseline_Est_Start_water <-   D5_Baseline_Est_Start_water$Baseline_Estimated_Starting_water
# 
# 
# D5_Frontier_Est_Start_water <- df_summer %>% 
#   filter(summer_deciles_names =="decile_5" ) %>% 
#   select(Frontier_Estimated_Starting_water)
# 
# D5_Frontier_Est_Start_water <- D5_Frontier_Est_Start_water$Frontier_Estimated_Starting_water
# 
# 
# 
# 
# 
# print(paste0("D5_Baseline_Est_Start_water = ", D5_Baseline_Est_Start_water))
# print(paste0("D5_Frontier_Est_Start_water = ", D5_Frontier_Est_Start_water)) 
```

## Calulate a number of variables:

* Creates 2 new df; baseline forecast yield and frontier forecast yield
* The below is an example of for one date which contains the below steps for checking.
* after this section a loop will run through a function retaining only the forecast yield by date. 

* **Baseline**

* summer_rain_decile5 = Add the summer rainfall for decile 5

* 1. `PAW` (for decile 5) = 25% of summer rainfall 
* 2. `rainfall_to_date` = amount of rainfall from 1/4 to defined date 
* 3. `rainfall_to_end_GS` = *not sure what this is, perhaps its the amount of rainfall in GS - rainfall to defined date*
* 4. `estimated_crop_water_use` (mm) = `PAW` + `rainfall_to_date` 
* 5. `Evaporation_on_term` = `estimated_crop_water_use` * 0.267 + 11.7
* 6. `Baseline_TE_term` = 21
* 7. `PY` (Potential Yield) = ((`estimated_crop_water_use` - `Evaporation_on_term`)* `Baseline_TE_term`)/1000
* 8. Yield_forecast = 80% * `PY` 



###### The first code chunk is the baseline values and calulations

* Kenton please check the calculation 
* This is a worked example for one date at the start of the GS
* If you want to change the date modified the first line in the below code chunk
* from "\\fs1-cbr.nexus.csiro.au\{af-sandysoils-ii}\work\Output-2\Analysis\Scripts\Jackie\rainfall and yld potentail\SSO2_CopevilleCore_FertandYieldBudget_2024_jaxs.xlsx"

```{r append cals Baseline, echo=FALSE}

defined_date <- defined_date1

df_gs_baseline_values <- df_gs %>% select(
  Station_name,
  Station_number,
  Years_included ,
  GS_period,
  GS_deciles_names, 
  GS_decile_max_rain
)
  
## get the rainfall for summer rainfall decile 5
summer_rain_decile5 <- df_summer %>% 
  filter(summer_deciles_names =="decile_5" ) %>% 
  select(summer_decile_max_rain)
summer_rain_decile5 <-   summer_rain_decile5$summer_decile_max_rain
#summer_rain_decile5
df_gs_baseline_values <- df_gs_baseline_values %>% mutate(summer_rain_decile5 = summer_rain_decile5)


# Est start water
df_gs_baseline_values <- df_gs_baseline_values %>%
  mutate(PAW = summer_rain_decile5*.25)


## get the rainfall to date
rainfall_to_date <- daily_file_sum_rain_all %>% 
  filter(Defined_date == defined_date ) %>% 
  select(sum_rain)
rainfall_to_date <-   rainfall_to_date$sum_rain
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(
    defined_date = defined_date,
    rainfall_to_date = rainfall_to_date
    )

## rainfall to maturity
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(rainfall_to_end_GS = GS_decile_max_rain - rainfall_to_date)


#Estimated_crop_water_use = `Baseline_Est_Start_water`  + `Rainfall_to_maturity`
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(estimated_crop_water_use = PAW + rainfall_to_end_GS)


#Baseline_Evaporation_on_term = `Baseline_Estimated_crop_water_use` * 0.267 + 11.7
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Evaporation_on_term = estimated_crop_water_use * 0.267 + 11.7)


#Baseline_TE_term = 21
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Baseline_TE_term = 21)


#Potential Yield (Baseline_PY) = ((`Baseline_Estimated_crop_water_use` - `Baseline_Evaporation_on_term`)* `Baseline_TE_term`)/1000
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(PY = ((estimated_crop_water_use - Evaporation_on_term)* Baseline_TE_term)/1000)


#Yield baseline = 80% * `Baseline_PY` 
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Yield_forecast = 0.8* PY)


df_gs_baseline_values <- df_gs_baseline_values %>% mutate(across(where(is.numeric), round, 2))
 
 DT::datatable(df_gs_baseline_values)
 

```
###### The second code chunk is the Frontier values and calulations

## Calulate a number of variables:

* **Frontier**

* summer_rain_decile5 = Add the summer rainfall for decile 5


* 1. `PAW` (for decile 5) = (25% of summer rainfall) + 6.
* 2. `rainfall_to_date` = amount of rainfall from 1/4 to defined date  
* 3. `rainfall_to_end_GS` = *not sure what this is, perhaps its the amount of rainfall in GS - rainfall to defined date*
* 4. `estimated_crop_water_use` (mm) = `PAW`  + `rainfall_to_end_GS`
* 5. `Evaporation_on_term` = `estimated_crop_water_use` * 0.18 + 15
* 6. `Front_TE_term` = 26
* 7. `PY` (Potential Yield Front) = ((`estimated_crop_water_use` - `Evaporation_on_term`)* `Front_TE_term`)/1000
* 8. `Yield_forecast` = 80% * `PY` 


* Kenton please check the calculation 
* This is a worked example for one date at the start of the GS
* If you want to change the date modified the first line in the below code chunk

```{r append cals Frontier, echo=FALSE}

defined_date <- defined_date1

df_gs_front_values <- df_gs %>% select(
  Station_name,
  Station_number,
  Years_included ,
  GS_period,
  GS_deciles_names, 
  GS_decile_max_rain
)
  
## get the rainfall for summer rainfall decile 5
summer_rain_decile5 <- df_summer %>% 
  filter(summer_deciles_names =="decile_5" ) %>% 
  select(summer_decile_max_rain)
summer_rain_decile5 <-   summer_rain_decile5$summer_decile_max_rain
#summer_rain_decile5
df_gs_front_values <- df_gs_front_values %>% mutate(summer_rain_decile5 = summer_rain_decile5)
#df_gs_front_values

# Est start water
df_gs_front_values <- df_gs_front_values %>%
  mutate(PAW = (summer_rain_decile5 *.25)+6)
  


## get the rainfall to date
rainfall_to_date <- daily_file_sum_rain_all %>% 
  filter(Defined_date == defined_date ) %>% 
  select(sum_rain)
rainfall_to_date <-   rainfall_to_date$sum_rain

df_gs_front_values <- df_gs_front_values %>% 
  mutate(
    defined_date = defined_date,
    rainfall_to_date = rainfall_to_date
    )

## rainfall to maturity
df_gs_front_values <- df_gs_front_values %>% 
  mutate(rainfall_to_end_GS = GS_decile_max_rain - rainfall_to_date)


#Estimated_crop_water_use = `Baseline_Est_Start_water` + `Rainfall_to_maturity`
df_gs_front_values <- df_gs_front_values %>% 
  mutate(estimated_crop_water_use = PAW + rainfall_to_end_GS)


#Baseline_Evaporation_on_term = `Baseline_Estimated_crop_water_use` * 0.18 + 15
df_gs_front_values <- df_gs_front_values %>% 
  mutate(Evaporation_on_term = estimated_crop_water_use * 0.18 + 15)


#Baseline_TE_term = 26
df_gs_front_values <- df_gs_front_values %>% 
  mutate(Front_TE_term = 26)


#Potential Yield (Baseline_PY) = ((`Baseline_Estimated_crop_water_use` - `Baseline_Evaporation_on_term`)* `Baseline_TE_term`)/1000
df_gs_front_values <- df_gs_front_values %>% 
  mutate(PY = ((estimated_crop_water_use - Evaporation_on_term)* Front_TE_term)/1000)


#Yield baseline = 80% * `Baseline_PY` 
df_gs_front_values <- df_gs_front_values %>% 
  mutate(Yield_forecast = 0.8* PY)

df_gs_front_values <- df_gs_front_values %>% mutate(across(where(is.numeric), round, 2))

DT::datatable(df_gs_front_values)
 

```

#### Run the above example for all the dates 
* use the 'daily_file_sum_rain' as input file for a loop but only keep the final yield
* data fame with dates method and yield

***Baseline forecast yield***
```{r append cals loop base, echo=FALSE, message=FALSE, warning=FALSE}
### create a function and loop through a list
defined_date_list <- daily_file_sum_rain_all$Defined_date
#defined_date_list <- c("2024-04-01", "2024-05-28")


for(defined_date_list in defined_date_list){
  
df_gs_baseline_values <- df_gs %>% select(
  Station_name,
  Station_number,
  Years_included ,
  GS_period,
  GS_deciles_names, 
  GS_decile_max_rain
)

## get the rainfall for summer rainfall decile 5
summer_rain_decile5 <- df_summer %>% 
  filter(summer_deciles_names =="decile_5" ) %>% 
  select(summer_decile_max_rain)
summer_rain_decile5 <-   summer_rain_decile5$summer_decile_max_rain
#summer_rain_decile5
df_gs_baseline_values <- df_gs_baseline_values %>% mutate(summer_rain_decile5 = summer_rain_decile5)


# Est start water
df_gs_baseline_values <- df_gs_baseline_values %>%
  mutate(PAW = summer_rain_decile5 *.25)
  


## get the rainfall to date
rainfall_to_date <- daily_file_sum_rain_all %>% 
  filter(Defined_date == defined_date_list ) %>% 
  select(sum_rain)
rainfall_to_date <-   rainfall_to_date$sum_rain
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(
    defined_date = defined_date_list,
    rainfall_to_date = rainfall_to_date
  )

## rainfall to maturity
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(rainfall_to_end_GS = GS_decile_max_rain - rainfall_to_date)


#Estimated_crop_water_use = `Baseline_Est_Start_water` + `Rainfall_to_maturity`
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(estimated_crop_water_use = PAW +  rainfall_to_end_GS)


#Baseline_Evaporation_on_term = `Baseline_Estimated_crop_water_use` * 0.267 + 11.7
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Evaporation_on_term = estimated_crop_water_use * 0.267 + 11.7)


#Baseline_TE_term = 21
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Baseline_TE_term = 21)


#Potential Yield (Baseline_PY) = ((`Baseline_Estimated_crop_water_use` - `Baseline_Evaporation_on_term`)* `Baseline_TE_term`)/1000
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(PY = ((estimated_crop_water_use - Evaporation_on_term)* Baseline_TE_term)/1000)


#Yield baseline = 80% * `Baseline_PY` 
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Yield_forecast = 0.8* PY)

## final dataset for outputs
forecast_yld <- df_gs_baseline_values %>% 
  select(GS_deciles_names, Yield_forecast, defined_date) %>% 
  mutate(method = "baseline")


name <- paste0("b_forecast_yld_", defined_date_list)
assign(name,forecast_yld)
}

## merge my forecast_yld file


b_forecast_yld <- rbind(`b_forecast_yld_2024-04-01` ,
                      `b_forecast_yld_2024-05-28` ,
                      `b_forecast_yld_2024-06-30` ,
                      `b_forecast_yld_2024-07-24` ,
                      `b_forecast_yld_2024-08-30` ,
                      `b_forecast_yld_2024-09-30` ,
                      `b_forecast_yld_2024-10-24`)
rm(`b_forecast_yld_2024-04-01` ,
   `b_forecast_yld_2024-05-28` ,
   `b_forecast_yld_2024-06-30` ,
   `b_forecast_yld_2024-07-24` ,
   `b_forecast_yld_2024-08-30` ,
   `b_forecast_yld_2024-09-30` ,
   `b_forecast_yld_2024-10-24`)
```

***Frontier forecast yield***
```{r append cals loop front, echo=FALSE, message=FALSE, warning=FALSE}

defined_date_list <- daily_file_sum_rain_all$Defined_date
#defined_date_list <- c("2024-04-01", "2024-05-28")


for(defined_date_list in defined_date_list){
  
   df_gs_front_values <- df_gs %>% select(
    Station_name,
    Station_number,
    Years_included ,
    GS_period,
    GS_deciles_names, 
    GS_decile_max_rain
  )
  
  ## get the rainfall for summer rainfall decile 5
  summer_rain_decile5 <- df_summer %>% 
    filter(summer_deciles_names =="decile_5" ) %>% 
    select(summer_decile_max_rain)
  summer_rain_decile5 <-   summer_rain_decile5$summer_decile_max_rain
  #summer_rain_decile5
  df_gs_front_values <- df_gs_front_values %>% mutate(summer_rain_decile5 = summer_rain_decile5)
  #df_gs_front_values
  
  # Est start water
  df_gs_front_values <- df_gs_front_values %>%
    mutate(PAW = (summer_rain_decile5*0.25)+6)
    
  
  
  ## get the rainfall to date
  rainfall_to_date <- daily_file_sum_rain_all %>% 
    filter(Defined_date == defined_date_list ) %>% 
    select(sum_rain)
  rainfall_to_date <-   rainfall_to_date$sum_rain
  
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(
      defined_date = defined_date_list,
      rainfall_to_date = rainfall_to_date
    )
  
  ## rainfall to maturity
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(rainfall_to_end_GS = GS_decile_max_rain - rainfall_to_date)
  
  
  #Estimated_crop_water_use = `Baseline_Est_Start_water`  + `Rainfall_to_maturity`
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(estimated_crop_water_use = PAW +  rainfall_to_end_GS)
  
  
  #Baseline_Evaporation_on_term = `Baseline_Estimated_crop_water_use` * 0.18 + 15
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(Evaporation_on_term = estimated_crop_water_use * 0.18 + 15)
  
  
  #Baseline_TE_term = 26
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(Front_TE_term = 26)
  
  
  #Potential Yield (Baseline_PY) = ((`Baseline_Estimated_crop_water_use` - `Baseline_Evaporation_on_term`)* `Baseline_TE_term`)/1000
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(PY = ((estimated_crop_water_use - Evaporation_on_term)* Front_TE_term)/1000)
  
  
  #Yield baseline = 80% * `Baseline_PY` 
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(Yield_forecast = 0.8* PY)
  
  ## final dataset for outputs
  forecast_yld <- df_gs_front_values %>% 
    select(GS_deciles_names, Yield_forecast, defined_date) %>% 
    mutate(method = "frontier")
    

  name <- paste0("f_forecast_yld_", defined_date_list)
  assign(name,forecast_yld)
}

## merge my forecast_yld file


f_forecast_yld <- rbind(`f_forecast_yld_2024-04-01` ,
                      `f_forecast_yld_2024-05-28` ,
                      `f_forecast_yld_2024-06-30` ,
                      `f_forecast_yld_2024-07-24` ,
                      `f_forecast_yld_2024-08-30` ,
                      `f_forecast_yld_2024-09-30` ,
                      `f_forecast_yld_2024-10-24`)
rm(`f_forecast_yld_2024-04-01` ,
   `f_forecast_yld_2024-05-28` ,
   `f_forecast_yld_2024-06-30` ,
   `f_forecast_yld_2024-07-24` ,
   `f_forecast_yld_2024-08-30` ,
   `f_forecast_yld_2024-09-30` ,
   `f_forecast_yld_2024-10-24`)



```


#### Append forecast yields for baseline and frointeir.

```{r join forecast yld base and front, echo=FALSE, message=FALSE, warning=FALSE}

b_f_forecast_yld <- rbind(b_forecast_yld, f_forecast_yld)
b_f_forecast_yld <- b_f_forecast_yld %>% mutate(across(where(is.numeric), round, 2))
DT::datatable(b_f_forecast_yld)

```
# Create plots of results

```{r pre plot work, echo=FALSE}


b_f_forecast_yld$GS_deciles_names <- factor(b_f_forecast_yld$GS_deciles_names , ordered = TRUE,
                                            levels = c("decile_1", "decile_2", "decile_3", "decile_4",
                                                       "decile_5", "decile_6", "decile_7", "decile_8",
                                                       "decile_9","decile_10" ))

# temp <-b_f_forecast_yld %>%
#   filter(GS_deciles_names == "decile_5")


plot1 <-b_f_forecast_yld %>%
  #filter(GS_deciles_names == "decile_5") %>%  
  ggplot(aes(x = defined_date , y = Yield_forecast, group=method) )+
  geom_point(aes(color=method))+
  geom_line(aes(color=method))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(.~GS_deciles_names )+
  labs(title = "Yield forecast",
       subtitle = paste0("Station name: ", distinct(df_gs, Station_name ),
                         " - ", distinct(df_gs, Station_number )),
       caption = paste0("Years included to make deciles : ", distinct(df_gs,Years_included),
                        ". GS period:",  distinct(df_gs,GS_period)),
       y = "Yield kg/ha",
       x = "",
       colour = "" #removed the legend title
  )
plot1


```




# Save file
* Saving to this folder.
* If it is in another location change the bellow code chuck.(file_path_input_data)
* "//fs1-cbr.nexus.csiro.au/{af-sandysoils-ii}/work/Output-2/Analysis/Scripts/Jackie/Forecast_ylds"



```{r save files, echo=FALSE}
path_saved_files <- file_path_input_data<-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Forecast_ylds")

ggsave(plot = plot1,
       filename = paste0(path_saved_files,"/Forecast_yld_plot_", site_selected, ".png" ),
       width = 20, height = 12, units = "cm")


write_csv(b_f_forecast_yld,
          file = paste0(path_saved_files,"/Forecast_yld_",site_selected, ".csv"))
```