---
title: "Step 2 creating decile tables basic"
author: "Jackie"
date: "2025-04-02"
output: html_document
---

```{r load_libary, include=FALSE}
library(ggplot2)
library(readxl)
library(tidyverse)
library(lubridate)
library(data.table)
library(stringr)
```

## How to defined the start and end of growing season
* The default is 1/4 (1st April) to 15/10 (15th Oct)
* If you want to change this modified the below code chunk.

```{r define start and end of GS, echo=FALSE}


Day_start_GS_rainfall <- 1
Month_start_GS_rainfall <- 4
    

Day_end_GS_rainfall <- 15
Month_end_GS_rainfall <- 10
      

```

## Choose what site you want to create decile table for.


```{r list of sites, echo=FALSE}
list_of_sites <- data.frame(
    Name = c("Karoonda", "Wharminda", "Copeville", "Walpeup" , "Bute", "Balaklava", "Annuello"), ### add more here when you have the info
    Number = c("25006", "18113", "25003", "76065", "21012", "21002", "76000"),
    Latitude = c("-35.09", "-33.97", "-34.80", "-35.14",  "-33.86", "-34.14", "-34.85"),
    Longitude = c("139.90", "136.25", "139.85", "142.02", "138.01", "138.42", "142.78"),
    State = c("SA", "SA", "SA", "VIC","SA", "SA", "VIC")
    )

DT::datatable(list_of_sites)

```


## List of files in step 1
* Looking in this folder.
* If it is in another location change the bellow code chuck.(file_path_input_data)
* "//fs1-cbr.nexus.csiro.au/{af-sandysoils-ii}/work/Output-2/Analysis/Scripts/Jackie/Downloaded_files"

```{r list of sites with decile tables, echo=FALSE}

 file_path_input_data<-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Downloaded_files")

list_of_file <- list.files(path = file_path_input_data, pattern = ".csv")
list_of_file <- as.data.frame(list_of_file)
DT::datatable(list_of_file)
 
```

## Select the site number
* create a new variable in the below code chuck that will be used for the analysis
* Shiny application would be nice but then I have problem saving the output.

```{r sites_selction, echo=FALSE}
 site_selected <- "25006"
print(site_selected)
```
## Download the **Neater met file**  

```{r sites_selction_download, echo=FALSE}

path <-  file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Downloaded_files")

df <- read.csv(paste0(path, "/Neater_file_", site_selected,  ".csv")) 
     
      ## add a clm with two dates marked as start and end
      df <- df %>% mutate(
        start_end_GS_date = case_when(
          month == Month_start_GS_rainfall & day_of_month == Day_start_GS_rainfall ~ "start_gs",
          month == Month_end_GS_rainfall & day_of_month == Day_end_GS_rainfall ~ "end_gs",
      TRUE ~ NA))
      
      ### fill the blanks

      df <- df %>% fill(start_end_GS_date) %>%
      mutate(
      season = case_when(
      start_end_GS_date == "start_gs" ~ "gs",
      TRUE ~ "summer"))

      df <- df %>% select(-start_end_GS_date)
``` 

#### Date range of file you have selected.
```{r sites_selction_date range, echo=FALSE}

#File start date and end date
paste("Start date in file is: ",
      min(df$Date),
      ". End date in file is: ",
      max(df$Date))
      
 
paste("Site Name (BOM): ", unique(df$Name),
      ". Site Number (BOM): ", unique(df$Number)
      )
           

GS_defined_as <- paste0(
  Day_start_GS_rainfall, "/", Month_start_GS_rainfall,
  " to ", Day_end_GS_rainfall, "/", Month_end_GS_rainfall)

paste("Growing season: ", GS_defined_as)
                
      
```  

### Do you want to use this full data set?
* The default is 1/1/1900 to 31/12/2023
* If you want to change it modify the below code chunk.

```{r subset date range, echo=FALSE}
start <- "1900-01-01"
end <- "2023-12-31"

### Filter dataset based on years 
df <- df %>% filter(between(Date, as.Date(start), as.Date(end)))

```

## Plot rain for each season type

```{r plot rain by season type, echo=FALSE, message=FALSE, warning=FALSE}


plot1 <- df %>%
    group_by(year, season) %>%
    summarise(sum_rain_season = sum(Rain, na.rm = TRUE)) %>%
    
    
    ggplot(aes(x = year, y = sum_rain_season, fill = season)) +
    geom_bar(stat = "identity") +
    labs(
      title = "Sum of rain per year",
      subtitle = paste0(
        "Station name: ",
        distinct(df, Name)
      ),
      
       caption = paste0("Years included : ",
                        year(min(df$Date)) ,
                        " to ",
                        year(max(df$Date)),
                       ". GS defined as: ", 
                         GS_defined_as),
      
      y = "sum of rain")
plot1

```

## GS decile table 

```{r decile table GS, echo=FALSE}



  
  gs_rain <- df %>%
    group_by(year, season) %>%
    summarise(sum_rain_season = sum(Rain, na.rm = TRUE)) %>%
    filter(season == "gs")
  
  ## 5a. GS ----------------------------------------------------------------------
#the percentiles for each year.

GS_decile_max_rain <- quantile(gs_rain$sum_rain_season, c(.1, .2, .3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0))
GS_deciles_names <- c("decile_1", "decile_2", "decile_3", "decile_4", "decile_5", "decile_6", "decile_7", "decile_8", "decile_9", "decile_10")

GS_decile_table <- data.frame(GS_decile_max_rain, GS_deciles_names, row.names = NULL)
GS_decile_table <- mutate(GS_decile_table, GS_decile_min_rain = lag(GS_decile_max_rain+0.1))


#add in the min value to table
GS_decile_table[1,3] <-  min(gs_rain$sum_rain_season)
GS_decile_table <- GS_decile_table %>%  select (GS_deciles_names, GS_decile_min_rain, GS_decile_max_rain)


 GS_decile_table <- GS_decile_table %>% 
   mutate(Station_name = unique(df$Name),
          Station_number = unique(df$Number),
           Years_included = paste0(
                                   year(min(df$Date)) ,  " to ", 
                                   year(max(df$Date))),
          GS_period =   GS_defined_as)
          
                         

GS_decile_table_df <- as.data.frame(GS_decile_table)
GS_decile_table_df <- GS_decile_table_df %>% mutate(across(where(is.numeric), round, 2))
#won't save because its reactive - I cant work it out

DT::datatable(GS_decile_table_df)

```