---
title: "Step 4 Yield potential for current season"
author: "Jackie"
date: "2025-03-31"
output: html_document
---

```{r load_libary, include=FALSE}
library(ggplot2)
library(readxl)
library(tidyverse)
library(lubridate)
library(data.table)
library(stringr)
library(DT)
```

# Workflow for analysing climate data creating decile tables and forecasting yields.
* Series of R markdown. Best to run these in order, but once you have historical yields step 2 and 3 they don’t need to be repeated to get a yield forecast.  
**Step 1** 
 *	Download patch point met file, tidy up and saved to directory. User to specify the site number.  
**Step 2** 
*	User defined site, and ‘season’.
*	Create plot sum of rain, per year, per season for site selected
*	Create historical files 1. Decile table for GS. 2. Decile table summer season.
*	File for each year with sum of rain per year and season type.  
**Step 3**
*	User defined site creates yield potential for decile years, using baseline and frontier approach.
*	Creates plot  
**Step 4**
*	User defined site creates yield forecast for decile years, using baseline and frontier approach for defined dates
*	Creates plot  


## Choose what site you want to create forecast yield for.


```{r list of sites, echo=FALSE}
list_of_sites <- data.frame(
    Name = c("Karoonda", "Wharminda", "Copeville", "Walpeup" , "Bute", "Balaklava", "Annuello"), ### add more here when you have the info
    Number = c("25006", "18113", "25003", "76065", "21012", "21002", "76000"),
    Latitude = c("-35.09", "-33.97", "-34.80", "-35.14",  "-33.86", "-34.14", "-34.85"),
    Longitude = c("139.90", "136.25", "139.85", "142.02", "138.01", "138.42", "142.78"),
    State = c("SA", "SA", "SA", "VIC","SA", "SA", "VIC")
    )

DT::datatable(list_of_sites)


 
```

## List of historical decile tables created in step 2
* Looking in this folder.
* If it is in another location change the bellow code chuck.(file_path_input_data)
* "//fs1-cbr.nexus.csiro.au/{af-sandysoils-ii}/work/Output-2/Analysis/Scripts/Jackie/Decile_tables"

```{r list of sites with decile tables, echo=FALSE}

 file_path_input_data<-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Decile_tables")

list_of_file <- list.files(path = file_path_input_data, pattern = ".csv")
list_of_file <- as.data.frame(list_of_file)
DT::datatable(list_of_file)
 
```
## Select the site number
* create a new variable in the below code chuck that will be used for the analysis
* Shiny application would be nice but then I have problem saving the output.

```{r sites_selction, echo=FALSE}
 site_selected <- "25006"
print(site_selected)
```
## Download the **daily met** file to calulate this years inputs
* 1. how much rain since the start of the GS
* use the daily met file to calculate the rain from start of growing season to defined date.

* 2. how much rain over 'summer month"
* use the daily met file to calculate the rain from 1/11 to 31/3.


```{r daily met file, echo=FALSE, warning=FALSE}
  daily_file <- read.csv(
    paste0(
    file_path_input_data,
         "/Daily_met_file_season types_",
         site_selected, 
         ".csv") )
daily_file <- daily_file %>% mutate(across(where(is.numeric), round, 2))

str(daily_file)
```
## 1. how much rain since the start of the GS.

* If the daily met file won't allow you to choose so many dates (ie the dates have not happened yet for that year).
* Make the dates the same for the subsequent defined date. 
* The report is expecting 8 dates, but maybe you only have 2 date, so you can fill out date1 and date2 with real dates that occur in the daily met file, the rest of the dates should then become the last know dates i.e. date2.
* You will need to **change the dates in the below code chunk** (if you don't want these).

* Notes that these dates will need to match what was used to create the historical GS decile tables with a fixed date.
* what year do you want to look at 

```{r define year, echo=FALSE}

### summer dates after GS
year <- "2023"
print(paste0("Year = ", year))
```

```{r sites_selction_download GS file, echo=FALSE, warning=FALSE}

start <- paste0(year, "-04-01")

defined_date1 <- paste0(year, "-04-01")
defined_date2 <- paste0(year, "-05-01")
defined_date3 <- paste0(year, "-06-01")
defined_date4 <- paste0(year, "-07-01")
defined_date5 <- paste0(year, "-08-01")
defined_date6 <- paste0(year, "-09-01")
defined_date7 <- paste0(year, "-10-01")
defined_date8 <- paste0(year, "-10-15")


### Filter dataset based on years 
daily_file1 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date1)))

daily_file2 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date2)))
daily_file3 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date3)))
daily_file4 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date4)))
daily_file5 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date5)))
daily_file6 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date6)))
daily_file7 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date7)))
daily_file8 <- daily_file %>% filter(between(Date, as.Date(start), as.Date(defined_date8)))



daily_file_sum_rain1 <- daily_file1 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date1, date = "date1")
daily_file_sum_rain2 <- daily_file2 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date2, date = "date2")
daily_file_sum_rain3 <- daily_file3 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date3, date = "date3")
daily_file_sum_rain4 <- daily_file4 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date4, date = "date4")
daily_file_sum_rain5 <- daily_file5 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date5, date = "date5")
daily_file_sum_rain6 <- daily_file6 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date6, date = "date6")
daily_file_sum_rain7 <- daily_file7 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date7, date = "date7")
 daily_file_sum_rain8 <- daily_file8 %>% summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% mutate(startGS =start, Defined_date =defined_date8, date = "date8")

daily_file_sum_rain_all_GS <- rbind(daily_file_sum_rain1,
                                 daily_file_sum_rain2,
                                 daily_file_sum_rain3,
                                 daily_file_sum_rain4,
                                 daily_file_sum_rain5,
                                 daily_file_sum_rain6,
                                 daily_file_sum_rain7,
                                 daily_file_sum_rain8
                                 )

rm(daily_file_sum_rain1,
   daily_file_sum_rain2,
   daily_file_sum_rain3,
   daily_file_sum_rain4,
   daily_file_sum_rain5,
   daily_file_sum_rain6,
   daily_file_sum_rain7,
   daily_file_sum_rain8,
   daily_file1,
   daily_file2,
   daily_file3,
   daily_file4,
   daily_file5,
   daily_file6,
   daily_file7,
   daily_file8)
### Summary of rain

daily_file_sum_rain_all_GS <- daily_file_sum_rain_all_GS %>% mutate(across(where(is.numeric), round, 2))
daily_file_sum_rain_all_GS <- daily_file_sum_rain_all_GS %>%  select(date, startGS, Defined_date, sum_rain)

DT::datatable(daily_file_sum_rain_all_GS)

```

## 2. how much rain over 'summer month"
* use the daily met file to calculate the rain from 1/11 to 31/3.
* note the year for this analysis is specified in below code chuck, if you want a different year change it here.

## How to defined the start and end of summer months and year
* The default is 1/11 (1st Nov) to 31/03 (31th March)
* If you want to change this modified the below code chunk.

```{r define start and end of summer months, echo=FALSE}


#before GS
start_of_summer_before_GS <- paste0(year,"-01-01")
end_of_summer_before_GS <- paste0(year,"-03-31") #?should this be 1/4

#after GS
start_of_summer_after_GS <- paste0(year,"-11-01")
end_of_summer_after_GS <- paste0(year,"-12-31")


print(paste0("start of summer months = ", start_of_summer_after_GS, " end of summer months = ",end_of_summer_before_GS ))
```


```{r cal the summer rainfall, echo=FALSE}

### Filter dataset based on summer months 
#before GS
daily_file1_summer <- daily_file %>% filter(between(Date, as.Date(start_of_summer_before_GS), as.Date(end_of_summer_before_GS)))
#after GS
daily_file2_summer <- daily_file %>% filter(between(Date, as.Date(start_of_summer_after_GS), as.Date(end_of_summer_after_GS)))

daily_file_summer <- rbind(daily_file1_summer, daily_file2_summer)
rm(daily_file1_summer, daily_file2_summer)

daily_file_summer_sum_rain <- daily_file_summer %>% 
  summarise(sum_rain = sum(Rain, na.rm = TRUE)) %>% 
  mutate(start_summer =start_of_summer_after_GS, 
         end_summer =end_of_summer_before_GS)



### Summary of summer rain
daily_file_summer_sum_rain <- daily_file_summer_sum_rain %>% select(
  start_summer, end_summer, sum_rain)
DT::datatable(daily_file_summer_sum_rain)

```


## Download the **Growing season** decile file that has the fixed dates for start of season

* Note these dates should be compatible with the dates used to summaries this years GS.

```{r sites_selction_download gs file, echo=FALSE, warning=FALSE}
#GS_decile_table_df_25006 

 df_gs <- read.csv(
  paste0(
    file_path_input_data,
    "/GS_decile_table_df_fixed_dates_",
    site_selected, 
    ".csv") )
df_gs <- df_gs %>% mutate(across(where(is.numeric), round, 2))


DT::datatable(distinct(df_gs, defined_date), caption = "List of dates used to define the start of GS, season end is the same",)

DT::datatable(df_gs)




```



## Add some of this years data to the histriocal GS rainfall data (with fixed dates)

* 1. This years GS for number of different dates

```{r add how much GS rain this year, echo=FALSE, warning=FALSE}
### make a new clm called Defined date from the date range clm defined_date.

#distinct(df_gs,defined_date )
#distinct(daily_file_sum_rain_all_GS,Defined_date )

df_gs <- df_gs %>% 
  mutate(Defined_date_common_year = case_when(
    defined_date == "from 1-4to 14-10" ~ paste0(year, "-04-01"),
    defined_date == "from 1-5to 14-10" ~ paste0(year, "-05-01"),
    defined_date == "from 1-6to 14-10" ~ paste0(year, "-06-01"),
    defined_date == "from 1-7to 14-10" ~ paste0(year, "-07-01"),
    defined_date == "from 1-8to 14-10" ~ paste0(year, "-08-01"),
    defined_date == "from 1-9to 14-10" ~ paste0(year, "-09-01"),
    defined_date == "from 1-10to 14-10" ~ paste0(year, "-10-01")
  ))

## join the decile GS historical data 
names(daily_file_sum_rain_all_GS)
df_gs <- left_join(df_gs , daily_file_sum_rain_all_GS,  by = join_by(Defined_date_common_year == Defined_date))

```

* 2. This years summer rainfall

```{r add how much GS rain this year, echo=FALSE, warning=FALSE}

### add this years summer rainfall
df_gs <- df_gs %>% 
  mutate(summer_rain_sum = daily_file_summer_sum_rain$sum_rain)


#rename some clm to make it clear
df_gs <- df_gs %>% rename(GS_rainfall_defined_date_historical =GS_decile_max_rain,
                          GS_rainfall_defined_date_current_yr = sum_rain,
                          summer_rain_current_yr = summer_rain_sum)


```



## Calulate a number of variables:

* Creates 2 new df; baseline forecast yield and frontier forecast yield
* The below is an example of for one date which contains the below steps for checking.
* after this section a loop will run through a function retaining only the forecast yield by date. 



* **Baseline**						
* 1. ` Estimated Starting Water (mm) = Summer rainfall *.25						
* 2. `Estimated Evaporation` = (Estimated Rainfall to maturity + GSR to date) *0.4						
* 3. `Estimated Water Supply` = (GS Rain + Estimated rainfall to maturity+ Estimated Starting water) - Estimated Evaporation						
* 4. `Estimated Yield Potential (kg/ha) = Estimated Water Supply *20						
* 5.  Yield_forecast = 80% * `EPY` 						







###### The first code chunk is the baseline values and calulations

* Kenton please check the calculation 
* This is a worked example for one date at the start of the GS
* If you want to change the date modified the first line in the below code chunk
* from "\\fs1-cbr.nexus.csiro.au\{af-sandysoils-ii}\work\Output-2\Analysis\Scripts\Jackie\rainfall and yld potentail\SSO2_CopevilleCore_FertandYieldBudget_2024_jaxs.xlsx"

```{r append cals Baseline, echo=FALSE}

df_gs <- df_gs %>% 
  mutate(est_sw_base = (summer_rain_current_yr*.25),
         
         est_evap_base = (GS_rainfall_defined_date_historical +GS_rainfall_defined_date_current_yr)*0.4,
         
         est_water_supp_base = ((GS_rainfall_defined_date_current_yr + 
                             GS_rainfall_defined_date_historical+ 
                             est_sw_base) -   est_evap_base),
         
         est_yp_base = (est_water_supp_base *20),
         Yld_forecast_base = (est_yp_base*.80)
         )


 
 df_gs_base <- df_gs %>% select(Defined_date_common_year, GS_deciles_names, GS_rainfall_defined_date_historical,
                               Station_name, Station_number, summer_rain_current_yr, GS_rainfall_defined_date_current_yr,
                               
                               est_sw_base,
                               est_evap_base,
                               est_water_supp_base,
                               est_yp_base,
                               Yld_forecast_base)
 
 df_gs_base <- df_gs_base %>% mutate(across(where(is.numeric), round, 2))
  DT::datatable(df_gs_base)

```

#### UP TO HERE ####

###### The second code chunk is the Frontier values and calulations

## Calulate a number of variables:

* **Frontier**

* summer_rain_decile5 = Add the summer rainfall for decile 5


* 1. `PAW` (for decile 5) = (25% of summer rainfall) + 6.
* 2. `rainfall_to_date` = amount of rainfall from 1/4 to defined date  
* 3. `rainfall_to_end_GS` = *not sure what this is, perhaps its the amount of rainfall in GS - rainfall to defined date*
* 4. `estimated_crop_water_use` (mm) = `PAW`  + `rainfall_to_end_GS`
* 5. `Evaporation_on_term` = `estimated_crop_water_use` * 0.18 + 15 ** this needs changing***
* 6. `Front_TE_term` = 26
* 7. `PY` (Potential Yield Front) = ((`estimated_crop_water_use` - `Evaporation_on_term`)* `Front_TE_term`)/1000
* 8. `Yield_forecast` = 80% * `PY` 


* Kenton please check the calculation 
* This is a worked example for one date at the start of the GS
* If you want to change the date modified the first line in the below code chunk

```{r append cals Frontier, echo=FALSE}

defined_date <- defined_date1

df_gs_front_values <- df_gs %>% select(
  Station_name,
  Station_number,
  Years_included ,
  GS_period,
  GS_deciles_names, 
  GS_decile_max_rain
)
  
## get the rainfall for summer rainfall decile 5
summer_rain_decile5 <- df_summer %>% 
  filter(summer_deciles_names =="decile_5" ) %>% 
  select(summer_decile_max_rain)
summer_rain_decile5 <-   summer_rain_decile5$summer_decile_max_rain
#summer_rain_decile5
df_gs_front_values <- df_gs_front_values %>% mutate(summer_rain_decile5 = summer_rain_decile5)
#df_gs_front_values

# Est start water
df_gs_front_values <- df_gs_front_values %>%
  mutate(PAW = (summer_rain_decile5 *.25)+6)
  


## get the rainfall to date
rainfall_to_date <- daily_file_sum_rain_all %>% 
  filter(Defined_date == defined_date ) %>% 
  select(sum_rain)
rainfall_to_date <-   rainfall_to_date$sum_rain

df_gs_front_values <- df_gs_front_values %>% 
  mutate(
    defined_date = defined_date,
    rainfall_to_date = rainfall_to_date
    )

## rainfall to maturity
df_gs_front_values <- df_gs_front_values %>% 
  mutate(rainfall_to_end_GS = GS_decile_max_rain - rainfall_to_date)


#Estimated_crop_water_use = `Baseline_Est_Start_water` + `Rainfall_to_maturity`
df_gs_front_values <- df_gs_front_values %>% 
  mutate(estimated_crop_water_use = PAW + rainfall_to_end_GS)


#Baseline_Evaporation_on_term = `Baseline_Estimated_crop_water_use` * 0.18 + 15
df_gs_front_values <- df_gs_front_values %>% 
  mutate(Evaporation_on_term = estimated_crop_water_use * 0.18 + 15)


#Baseline_TE_term = 26
df_gs_front_values <- df_gs_front_values %>% 
  mutate(Front_TE_term = 26)


#Potential Yield (Baseline_PY) = ((`Baseline_Estimated_crop_water_use` - `Baseline_Evaporation_on_term`)* `Baseline_TE_term`)/1000
df_gs_front_values <- df_gs_front_values %>% 
  mutate(PY = ((estimated_crop_water_use - Evaporation_on_term)* Front_TE_term)/1000)


#Yield baseline = 80% * `Baseline_PY` 
df_gs_front_values <- df_gs_front_values %>% 
  mutate(Yield_forecast = 0.8* PY)

df_gs_front_values <- df_gs_front_values %>% mutate(across(where(is.numeric), round, 2))

DT::datatable(df_gs_front_values)
 

```

#### Run the above example for all the dates 
* use the 'daily_file_sum_rain' as input file for a loop but only keep the final yield
* data fame with dates method and yield

***Baseline forecast yield***
```{r append cals loop base, echo=FALSE, message=FALSE, warning=FALSE}
### create a function and loop through a list
defined_date_list <- daily_file_sum_rain_all$Defined_date
#defined_date_list <- c("2024-04-01", "2024-05-28")


for(defined_date_list in defined_date_list){
  
df_gs_baseline_values <- df_gs %>% select(
  Station_name,
  Station_number,
  Years_included ,
  GS_period,
  GS_deciles_names, 
  GS_decile_max_rain
)

## get the rainfall for summer rainfall decile 5
summer_rain_decile5 <- df_summer %>% 
  filter(summer_deciles_names =="decile_5" ) %>% 
  select(summer_decile_max_rain)
summer_rain_decile5 <-   summer_rain_decile5$summer_decile_max_rain
#summer_rain_decile5
df_gs_baseline_values <- df_gs_baseline_values %>% mutate(summer_rain_decile5 = summer_rain_decile5)


# Est start water
df_gs_baseline_values <- df_gs_baseline_values %>%
  mutate(PAW = summer_rain_decile5 *.25)
  


## get the rainfall to date
rainfall_to_date <- daily_file_sum_rain_all %>% 
  filter(Defined_date == defined_date_list ) %>% 
  select(sum_rain)
rainfall_to_date <-   rainfall_to_date$sum_rain
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(
    defined_date = defined_date_list,
    rainfall_to_date = rainfall_to_date
  )

## rainfall to maturity
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(rainfall_to_end_GS = GS_decile_max_rain - rainfall_to_date)


#Estimated_crop_water_use = `Baseline_Est_Start_water` + `Rainfall_to_maturity`
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(estimated_crop_water_use = PAW +  rainfall_to_end_GS)


#Baseline_Evaporation_on_term = `Baseline_Estimated_crop_water_use` * 0.267 + 11.7
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Evaporation_on_term = estimated_crop_water_use * 0.267 + 11.7)


#Baseline_TE_term = 21
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Baseline_TE_term = 21)


#Potential Yield (Baseline_PY) = ((`Baseline_Estimated_crop_water_use` - `Baseline_Evaporation_on_term`)* `Baseline_TE_term`)/1000
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(PY = ((estimated_crop_water_use - Evaporation_on_term)* Baseline_TE_term)/1000)


#Yield baseline = 80% * `Baseline_PY` 
df_gs_baseline_values <- df_gs_baseline_values %>% 
  mutate(Yield_forecast = 0.8* PY)

## final dataset for outputs
forecast_yld <- df_gs_baseline_values %>% 
  select(GS_deciles_names, Yield_forecast, defined_date) %>% 
  mutate(method = "baseline")


name <- paste0("b_forecast_yld_", defined_date_list)
assign(name,forecast_yld)
}

## merge my forecast_yld file


b_forecast_yld <- rbind(`b_forecast_yld_2024-04-01` ,
                      `b_forecast_yld_2024-05-28` ,
                      `b_forecast_yld_2024-06-30` ,
                      `b_forecast_yld_2024-07-24` ,
                      `b_forecast_yld_2024-08-30` ,
                      `b_forecast_yld_2024-09-30` ,
                      `b_forecast_yld_2024-10-24`)
rm(`b_forecast_yld_2024-04-01` ,
   `b_forecast_yld_2024-05-28` ,
   `b_forecast_yld_2024-06-30` ,
   `b_forecast_yld_2024-07-24` ,
   `b_forecast_yld_2024-08-30` ,
   `b_forecast_yld_2024-09-30` ,
   `b_forecast_yld_2024-10-24`)
```

***Frontier forecast yield***
```{r append cals loop front, echo=FALSE, message=FALSE, warning=FALSE}

defined_date_list <- daily_file_sum_rain_all$Defined_date
#defined_date_list <- c("2024-04-01", "2024-05-28")


for(defined_date_list in defined_date_list){
  
   df_gs_front_values <- df_gs %>% select(
    Station_name,
    Station_number,
    Years_included ,
    GS_period,
    GS_deciles_names, 
    GS_decile_max_rain
  )
  
  ## get the rainfall for summer rainfall decile 5
  summer_rain_decile5 <- df_summer %>% 
    filter(summer_deciles_names =="decile_5" ) %>% 
    select(summer_decile_max_rain)
  summer_rain_decile5 <-   summer_rain_decile5$summer_decile_max_rain
  #summer_rain_decile5
  df_gs_front_values <- df_gs_front_values %>% mutate(summer_rain_decile5 = summer_rain_decile5)
  #df_gs_front_values
  
  # Est start water
  df_gs_front_values <- df_gs_front_values %>%
    mutate(PAW = (summer_rain_decile5*0.25)+6)
    
  
  
  ## get the rainfall to date
  rainfall_to_date <- daily_file_sum_rain_all %>% 
    filter(Defined_date == defined_date_list ) %>% 
    select(sum_rain)
  rainfall_to_date <-   rainfall_to_date$sum_rain
  
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(
      defined_date = defined_date_list,
      rainfall_to_date = rainfall_to_date
    )
  
  ## rainfall to maturity
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(rainfall_to_end_GS = GS_decile_max_rain - rainfall_to_date)
  
  
  #Estimated_crop_water_use = `Baseline_Est_Start_water`  + `Rainfall_to_maturity`
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(estimated_crop_water_use = PAW +  rainfall_to_end_GS)
  
  
  #Baseline_Evaporation_on_term = `Baseline_Estimated_crop_water_use` * 0.18 + 15
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(Evaporation_on_term = estimated_crop_water_use * 0.18 + 15)
  
  
  #Baseline_TE_term = 26
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(Front_TE_term = 26)
  
  
  #Potential Yield (Baseline_PY) = ((`Baseline_Estimated_crop_water_use` - `Baseline_Evaporation_on_term`)* `Baseline_TE_term`)/1000
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(PY = ((estimated_crop_water_use - Evaporation_on_term)* Front_TE_term)/1000)
  
  
  #Yield baseline = 80% * `Baseline_PY` 
  df_gs_front_values <- df_gs_front_values %>% 
    mutate(Yield_forecast = 0.8* PY)
  
  ## final dataset for outputs
  forecast_yld <- df_gs_front_values %>% 
    select(GS_deciles_names, Yield_forecast, defined_date) %>% 
    mutate(method = "frontier")
    

  name <- paste0("f_forecast_yld_", defined_date_list)
  assign(name,forecast_yld)
}

## merge my forecast_yld file


f_forecast_yld <- rbind(`f_forecast_yld_2024-04-01` ,
                      `f_forecast_yld_2024-05-28` ,
                      `f_forecast_yld_2024-06-30` ,
                      `f_forecast_yld_2024-07-24` ,
                      `f_forecast_yld_2024-08-30` ,
                      `f_forecast_yld_2024-09-30` ,
                      `f_forecast_yld_2024-10-24`)
rm(`f_forecast_yld_2024-04-01` ,
   `f_forecast_yld_2024-05-28` ,
   `f_forecast_yld_2024-06-30` ,
   `f_forecast_yld_2024-07-24` ,
   `f_forecast_yld_2024-08-30` ,
   `f_forecast_yld_2024-09-30` ,
   `f_forecast_yld_2024-10-24`)



```


#### Append forecast yields for baseline and frointeir.

```{r join forecast yld base and front, echo=FALSE, message=FALSE, warning=FALSE}

b_f_forecast_yld <- rbind(b_forecast_yld, f_forecast_yld)
b_f_forecast_yld <- b_f_forecast_yld %>% mutate(across(where(is.numeric), round, 2))
DT::datatable(b_f_forecast_yld)

```
# Create plots of results

```{r pre plot work, echo=FALSE}


b_f_forecast_yld$GS_deciles_names <- factor(b_f_forecast_yld$GS_deciles_names , ordered = TRUE,
                                            levels = c("decile_1", "decile_2", "decile_3", "decile_4",
                                                       "decile_5", "decile_6", "decile_7", "decile_8",
                                                       "decile_9","decile_10" ))

# temp <-b_f_forecast_yld %>%
#   filter(GS_deciles_names == "decile_5")


plot1 <-b_f_forecast_yld %>%
  #filter(GS_deciles_names == "decile_5") %>%  
  ggplot(aes(x = defined_date , y = Yield_forecast, group=method) )+
  geom_point(aes(color=method))+
  geom_line(aes(color=method))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(.~GS_deciles_names )+
  labs(title = "Yield forecast",
       subtitle = paste0("Station name: ", distinct(df_gs, Station_name ),
                         " - ", distinct(df_gs, Station_number )),
       caption = paste0("Years included to make deciles : ", distinct(df_gs,Years_included),
                        ". GS period:",  distinct(df_gs,GS_period)),
       y = "Yield kg/ha",
       x = "",
       colour = "" #removed the legend title
  )
plot1


```




# Save file
* Saving to this folder.
* If it is in another location change the bellow code chuck.(file_path_input_data)
* "//fs1-cbr.nexus.csiro.au/{af-sandysoils-ii}/work/Output-2/Analysis/Scripts/Jackie/Forecast_ylds"



```{r save files, echo=FALSE}
path_saved_files <- file_path_input_data<-file.path("H:","Output-2", "Analysis", "Scripts", "Jackie", "Forecast_ylds")

ggsave(plot = plot1,
       filename = paste0(path_saved_files,"/Forecast_yld_plot_", site_selected, ".png" ),
       width = 20, height = 12, units = "cm")


write_csv(b_f_forecast_yld,
          file = paste0(path_saved_files,"/Forecast_yld_",site_selected, ".csv"))
```